Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Updated Figure 10

# trimesh_two_curvy_removed1 <- ggplot() +
#   geom_segment(data = tr_from_to_df_two_curvy3,
#                aes(
#                  x = x_from,
#                  y = y_from,
#                  xend = x_to,
#                  yend = y_to),
#                colour = "#000000")+
#   geom_point(data = umap_two_curvy_scaled,
#              aes(
#                x = UMAP1,
#                y = UMAP2
#              ),
#              color = "#636363",
#             alpha = 0.5,
#             size = 0.5
#             ) +
#   coord_equal() +
#   interior_annotation("c", position = c(0.92, 0.95))

@@

```{r}
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal."
#| fig-height: 10
#| fig-width: 15

free(distance_hist) / wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1_with_data, ncol = 3) 
```

>>>>

trimesh_two_curvy_removed1 <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy3,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000")+
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#636363",
            alpha = 0.5,
            size = 0.5
            ) +
  coord_equal() +
  interior_annotation("c", position = c(0.92, 0.95))

@@

```{r}
#| fig-cap: "Distribution of edge lengths and wireframes in \\gD{} and $7\\text{-}D$ with Delaunay triangulation, and two choices of long edge removal."
#| fig-height: 15
#| fig-width: 15

free(distance_hist) / wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model, ncol = 3) 
```
